An Improved Metric for the Analysis of Swarms

### 2018-04-18 paper.tex
Minors

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=6cm]{figures/FLOOD1}
{Flood fill Start.\label{emerge:FLOOD1}}

>>>>

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=6cm]{figures/FLOOD0}
{Flood fill Start.\label{emerge:FLOOD0}}

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=6cm]{figures/FLOOD1}
{Data Capture Start.\label{emerge:FLOOD1}}
